NumPy---Array Computation for Python

### 2019-12-19 paper.tex
Edit first four sections

NumPy is currently maintained by a group of 23 contributors with commit rights
to the NumPy code base. Out of these 17 maintainers were active in 2019.
Additionally, there are a few long term developers who contributed and maintain
specific parts of NumPy, but are not officially maintainers.
At a release cycle of about every half year, the five recent releases in the years
2018 and 2019 have averaged about 450~pull requests~(PR) each.\footnote{
    Note that before mid 2011, NumPy development did not happen on \url{github.com}.
    All data provided here is based on the development which happened through github
    pull requests. In some cases contributions by maintainers may not be categorized as such.}
% Since 1.14.0 (based on changelog): 381 + 438 + 490 + 531 + 402; last is preliminary
With each release attracting more than a hundred new contributors.

@@

The stacked plot in Figure~\ref{fig:prs-over-time} shows the number of
PR merged into the NumPy master branch.
In this plot PR opened by current and old maintainers are indicated.
Although the number of PRs being merged fluctuates,
the plot indicates an increased number of contributions over the past
years.
Over the course of its history, NumPy has attracted PR by 823 contributors.
However, its development still relies heavily on a relatively small number
of active maintainers, who share more than half of the contributions among
themselves.

% https://mail.python.org/pipermail/numpy-discussion/2015-October/073849.html
% https://github.com/numpy/numpy/pull/6352
NumPy adopted an official Governance Document on October~5,
2015\cite{NumPyProjectGovernance}.
Project decisions are usually made by consensus of interested contributors.
This means for many thing everyone is entrusted with veto power.
A Steering Council, currently composed of 12~members, facilitates this
process and oversees daily development of the project by contributing code
and reviewing contributions from the community.

% https://mail.python.org/pipermail/numpy-discussion/2018-July/078476.html
% https://github.com/numpy/numpy/pull/11865
NumPy's official Code of Conduct was approved on September~1, 2018\cite{NumPyCodeofConduct}.
In brief, we strive to:
\emph{be open};
\emph{be empathetic, welcoming, friendly, and patient};
\emph{be collaborative};
\emph{be inquisitive}; and
\emph{be careful in the words that we choose}.
The Code of Conduct also specifies how breaches can be reported and outlines
the process for responding to such reports.

>>>>

\subsection*{Governance}

% incl. CoC

\subsection*{Maintainers and contributors}

%  nr of core devs / commit rights) & contributors

NumPy is currently maintained a group of 23 contributors with commit rights
to the NumPy code base. Out of these 17 maintainers were active in 2019.
Additionally, there are a few long term developers who contributed and maintain
specific parts of NumPy, but are not officially maintainers.
At a release cycle of about every half year, the five recent releases in the years
2018 and 2019 have averaged about 450~pull requests~(PR) each.\footnote{
    Note that before mid 2011, NumPy development did not happen on \url{github.com}.
    All data provided here is based on the development which happened through github
    pull requests. In some cases contributions by maintainers may not be categorized as such.}
% Since 1.14.0 (based on changelog): 381 + 438 + 490 + 531 + 402; last is preliminary
With each release attracting more than a hundred new contributors.

@@

The stacked plot in Figure~\ref{fig:prs-over-time} shows the number of
PR merged into the NumPy master branch.
In this plot PR opened by current and old maintainers are indicated.
Although the number of PRs being merged fluctuates,
the plot indicates an increased number of contributions over the past
years.
Over the course of its history, NumPy has attracted PR by 823 contributors.
However, its development still relies heavily on the relative small number
of stable maintainers, who share more than half of the contributions among
themselves.

% may be useful:
% - https://github.com/docathon/watchtower
% - https://github.com/machine-shop/oss_devkit/blob/master/plot_pr.py % (PR over time plot, there may be other better versions out there)
